Re-finding to support a Deep Web Question Answering System

### 2010-03-05 trunk/paper/semsearch10/content/ontological_realms.tex
more fixes

\section{Representing and Ontological Realms}
Two types of ontologies are used by our system:
\begin{enumerate}
\item Realm ontologies, comprising a heterarchy of categories that
  characterize terms appearing in queries.
\item SSQ ontologies, describing the form of particular
  realm-specific queries.
\end{enumerate}
For any particular ontological realm, the number of potential
terms and their associated categories can be quite large.
Construction of a realm ontology and the terms associated
with its categories would be an extremely laborious task
for any non-trivial realm. For example, the realm of automobiles (which
we use for illustration in this paper) contains 
over XXXX categories and XXXX terms. We were unable to find
an appropriate ontology for this realm, so we constructed it
using categories from the DBPedia \cite{Auer07dbpedia:a}.
The primary benefit of using the DBPedia for this purpose is
that not only does it supply a categorical heterarchy, but it
also links to Wikipedia documents which provides us with a large
realm-specific document corpus.

@@

Once the semantic heterarchy is created, the next step is to create
training data for the system. The task is then to grab the pages,
build a corpus relating to a given category, and then compile the
information in a meaningful way. The overall goal is to grab enough
information to properly characterize a category while limiting the
amount of unnecessary content within the corpus. The problem with this
approach is the page density varies greatly across the
heterarchy. Each category within the DBpedia/Wikipedia heterarchy
contains a set of information pages, P, corresponding to the concepts
shared by the category. Since the categorical structure is a directed
acyclic graph \cite{Suchanek07yago:a}, we use of a Markov Blanket
\cite{Friedman97bayesiannetwork} to describe a particular
category. Our assumption is that a node can be fully described by its
ancestor, descendant, and spousal nodes (parent node of subcategory
not equal to the category). While this does not completely solve the
issue of a category residing in a sparse area of the graph, the amount
of information that can be obtained per blanket is usually more
helpful than per category.

The subcategories of the category Automobiles (Driving, Traffic Law,
Automobiles by Decade, and Auto Racing) can be seen as grabbing
information specific to the category. The super categories (Road
Vehicles) place the category in a higher perspective, abstractly
describing basketball as a concept. The spousal categories
(...Motor Sport, Individual Sport...) are an abstract description of
the subcategories.

Clustering the categories alone does not guarantee adequate corpus
creation. Since the above model relies on the subcategories to
describe specifics of a given category, the ideal situation would be
that the subcategories have many more pages than the super categories
and that there is a significant amount of information per page.  In
the case of Wikipedia, there are an average of 25.7 pages per category
\cite{1321474}. The assumption for collecting the training data is the
more subcategory data we have, the more detailed our description of
our category. Considering that there are many categories that have
much more than 26 pages, we instituted a PlusOne mechanism to extract
extra information. This mechanism checks if a subcategory has an
adequate number of pages α to fully describe its subtopic. We set this
number to ten times the average, or 260. $Level$ represents how many
extra levels we are to go down in the hierarchy, if
necessary. SubjectSet is the overall set of all pages associated with
the blanket structure along with any plusOne subjects obtained.

\begin{lstlisting}[language=Python, frame=none, tabsize=2, caption=BlanketSubjectRetreival, label=BlanketSubjectRetreival, basicstyle=\small]
def BlanketSubjectRetreival(blanket, maxLevel):
	for category in blanket:
		subjectSet.add(grabsubjects(category))
		diff = afterSize - beforeSize
		if diff <= a and category is subcategory:
			PlusOneMechanism(category, maxLevel)
	return subjectSet
\end{lstlisting}

\begin{lstlisting}[language=Python, frame=none, tabsize=2, caption=PlusOneMechanism, label=PlusOneMechanism, basicstyle=\small]
def PlusOneMechanism(category, level):
	plusOneSet = grabPlusOneSubcategories(category)
	for subcategory in plusOneSet:
		subject.add(grabSubjects(subcategory))
		diff = afterSize - beforeSize
		if diff <= a and level > 0:
			PlusOneMechanism(subcategory, level-1)

\end{lstlisting}

@@

The overall mechanism does not take into account the amount of
information within each page, but generally that can be ignored when
considering the size of the blanket corpus when we extract the text
from the Wikipedia subject pages. Using this method on the category
Automobiles, we can construct a corpus of 2255 subject pages and
6,084,260 terms.

When a category's corpus is built, we then build our n-gram frequency
distributions and store them in a database for the NLP processing. For
the purpose of calculating term importance to a blanket, we aggregate
the frequencies of all blankets and store this information as
well. For this system, term importance refers to the prior probability
of a category given an n-gram. We calculate this using Bayes Rule,
since we can easily obtain the n-gram-category and n-gram-vocabulary
probabilities. The higher the probability, the more likely a term is
referring to a category.

>>>>

\section{Representing and Ontological Realms}
Two types of ontologies are used by our system:
\begin{enumerate}
\item Realm ontologies, comprising a heterarchy of categories that
  characterize terms appearing in queries.
\item SSQ ontologies, describing the form of particular
  realm-specific queries.
\end{enumerate}
For any particular ontological realm, the number of potential
terms and their associated categories can be quite large.
Manual construction of a realm ontology and the terms associated
with its categories would be an extremely laborious task
for any non-trivial realm. For example, the realm of vehicles
in our current ontology contains 32 categories and millions of terms.
We were unable to find
an existing ontology for this realm, so we constructed one
using categories from the DBPedia \cite{Auer07dbpedia:a}.
The primary benefit of using the DBPedia for this purpose is
that not only does it supply a categorical heterarchy, but it
also links to Wikipedia documents which provide us with a large
realm-specific corpus.

@@

Once the semantic heterarchy is created, the next step is to create
training data for the system. To do this, we extract words from the pages,
thus building a corpus related to a given category.
Finally, we have compiled enough information to properly characterize
a category while limiting the
amount of unnecessary content within the corpus. The problem with this
approach is the page density varies greatly across the
heterarchy. Each category within the DBpedia and Wikipedia heterarchy
contains a set of information pages, P, corresponding to the concepts
shared by the category. Since the categorical structure is a directed
acyclic graph \cite{Suchanek07yago:a}, we use of a Markov Blanket
\cite{Friedman97bayesiannetwork} to describe a particular
category. We hypothesize that the terms associated with a category
can be found by identifying those terms associated with that category's
ancestor, descendant, and spousal nodes (i.e., other parent nodes of a subcategory). While this does not completely solve the
issue of a category residing in a sparse area of the graph, the amount
of information that can be obtained per blanket is more
helpful than per category.

Clustering the categories alone does not guarantee adequate corpus
creation. Since our model relies on the subcategories to
to provide terms associated with a given category, it will fail if
the subcategories do not provide enough data to our corpus.
For the purpose of gathering training data having more subcategory data
yields a more representative collection of terms for that category. 
The average number of pages per category in the Wikipedia is 25.7\cite{1321474}.
We have found that this number of pages is insufficient to provide a representative collection of terms for a category.
In order to gain more pages and expand the term base, we have used a
PlusOne mechanism to extract
extra information. This mechanism checks if a subcategory has an
adequate number of pages to fully describe its subtopic.
We have chosen this number to be approximately ten times the average
number of Wikipedia pages per category, or 260.  If a cateogory
does not contain the required number of pages, PlusOne continues to
search another level deeper in the hierarchy until a sufficient
number of pages has been reached.

@@

Our approach to category corpus construction does not take into
account the number of words contained within each page.
However, we have found this method to be adequate to construct
usable corpora. For example, when executed on the vehicle ontology,
this method yields 2255 subject pages and a corpus containing
1,691,727 unique terms and 6,084,260 total words.

After a category's corpus is built, we then build term frequency
distributions and store them in a database for natural language processing.
For this system, term importance refers to the prior probability
of a category given a term. We calculate this using Bayes Rule,
since we can easily obtain the term-category and term-corpus
probabilities. The higher the probability, the more likely a term is
referring to a category.
